\documentclass[11pt]{article}
\usepackage[margin=0.95in]{geometry}
\usepackage{fontspec}
\setmainfont[
            Extension=.ttf,
            UprightFont=NotoSans-Regular,
            BoldFont=NotoSans-Bold,
            ItalicFont=NotoSans-Italic,
            Ligatures=TeX
            ]{notosans}
\usepackage{multicol}
\usepackage{enumitem}
\usepackage[compact]{titlesec}
\usepackage{microtype}

\titlespacing*{\section}{0pt}{1.5\baselineskip}{0.5\baselineskip}
\titlespacing*{\subsection}{0pt}{0.5\baselineskip}{0pt}
\titlespacing*{\subsubsection}{0pt}{0pt}{0pt}
\titleformat{\subsubsection}
       {\normalfont\itshape}
       {\thesubsection}{1em}{}

\setlength\parindent{0pt}
\setlength\columnsep{24pt}

\author{Clement Lee}
\title{Resume}
\begin{document}
\pagenumbering{gobble}
\vspace*{1.5em}

{\huge\textbf{CLEMENT LEE}}
\vspace{0.25\baselineskip}

clem@princeton.edu

(801) 289-6300

clementl.com

\vspace{\baselineskip}
\begin{multicols}{2}
%********************EDUCATION********************
\section*{EDUCATION}
\subsection*{Princeton University\hfill\textnormal{2013---2017}}
\subsubsection*{Computer Science, B.S.E.\hfill\textnormal{3.75 GPA}\\
Certificate in Applied Mathematics}

Relevant coursework includes:
\begin{itemize}[noitemsep,nolistsep,leftmargin=*]
\item COS217 Programming Systems
\item COS226 Data Structures and Algorithms
\item COS445 Game Theory
\end{itemize}

\subsection*{University of Utah\hfill\textnormal{2009---2013}}
\subsubsection*{Computer Science/Mathematics\hfill\textnormal{3.84 GPA}}
Took mathematics and computer science courses since freshman year of high school due to having exhausted available options.

\subsection*{West High School\hfill\textnormal{2009---2013}}
\subsubsection*{Honors and IB Diploma\hfill\textnormal{4.43 GPA}}
\vspace{1.5\baselineskip}

%********************EXPERIENCE********************
\section*{EXPERIENCE}
\subsection*{R\&D Software Intern\hfill\textnormal{06/15---08/15}}
\subsubsection*{Microsoft}
Full-stack development on a variety of technologies.

\subsection*{R\&D Software Intern\hfill\textnormal{06/14---08/14}}
\subsubsection*{Bloomberg L.P.}
Developed natural language processing algorithms to automate live text analysis and question answering in C++ and Python.

\subsection*{Lab TA\hfill\textnormal{01/15---present}}
\subsubsection*{Princeton University Computer Science Dept.}
Tutoring and aiding computer science students in completing assignments and understanding fundamental concepts.

\subsection*{Web Editor\hfill\textnormal{02/15---present}}
\subsubsection*{Daily Princetonian}
Maintaining and developing the website of Princeton's largest student publication.

\subsection*{Full-Stack Developer\hfill\textnormal{01/14---12/14}}
\subsubsection*{Princeton MUN Conference}
Designed a new registration and live administration system to assist in conference organization using PHP.

\subsection*{IT Chair\hfill\textnormal{12/13---01/15}}
\subsubsection*{Princeton Student Government}
Maintained servers and developed student apps for the entirety of the Princeton student body in tandem with school administrators.

\subsection*{Backend Developer\hfill\textnormal{01/14---05/14}}
\subsubsection*{Read Record Replay}
Developed the server of a new website with Node.js for an educational nonprofit teaching English to young children using audiobooks.

%********************PROJECTS********************
\section*{PROJECTS}
\vspace{-0.5\baselineskip}
\subsubsection*{See github.com/clementlee.}

\vspace{2\baselineskip}
%\subsection*{WhenIsBad}
%i don't have projects...


%********************SKILLS********************
\section*{SKILLS}

\subsection*{Programming}
Familiar with a variety of different languages, which include C/C{}\verb!++!, Java/C\#, Python, and HTML/CSS/JS.

Adept at picking up new technology.

\subsection*{Mathematics}
Experience in topology, partial differential equations, abstract algebra, and more.

\subsection*{Miscellaneous Interests}
Photography, graphic design, and film.

\end{multicols}


\end{document}
